systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2004-11-16 paper/trunk/systemfit.tex
made small changes because my code section wouldn't compile. argh.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@565 591db2bd-e0a0-4d22-8c19-2192dbb7da31
question about nlsystemfit code section (example)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@566 591db2bd-e0a0-4d22-8c19-2192dbb7da31

@@

\section{CVS Revision Log}
\begin{verbatim}
$Log$
Revision 1.5  2004/11/16 05:31:19  hamannj
added cvs header and log section. to be removed when submitted.

\begin{verbatim}

>>>>

%% Arne -- Did you put the ~'s in by hand?

@@

\section{CVS Revision Log}
\begin{verbatim}
$Log$
Revision 1.7  2004/11/16 05:34:47  hamannj
question about nlsystemfit code section (example)

Revision 1.6  2004/11/16 05:32:46  hamannj
made small changes because my code section wouldn't compile. argh.

Revision 1.5  2004/11/16 05:31:19  hamannj
added cvs header and log section. to be removed when submitted.

\end{verbatim}
